---
output: github_document
bibliography: 'citation_README.bib'
csl: '/Users/Primahadi/Google Drive/MONASH PhD Journey/3rd Year (mid 2017-mid 2018)/ch6/apa-old-doi-prefix.csl'
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

**Authors:** [Gede Primahadi Wijaya Rajeg](https://figshare.com/authors/Gede_Primahadi_Wijaya_Rajeg/1234749)<br/>
**License:** [GPL-2](https://www.gnu.org/licenses/old-licenses/gpl-2.0.en.html)<br/>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# happyr

The goal of `happyr` is to provide the R functionalities and the required dataset for the quantitative analyses in Rajeg [-@rajeg_metaphorical_2018]. The underlying codes within the package are based on most of the core packages of the [`tidyverse`](https://www.tidyverse.org).

## Installation

You can install the released version of `happyr` from [GitHub](https://github.com/gederajeg/happyr) with the [`remotes`](https://github.com/r-lib/remotes) package:

``` r
# install the `remotes` package
install.packages("remotes") 

# install the `happyr` package
remotes::install_github("gederajeg/happyr@v0.1.0") 
```

## Examples

### Interrater-agreement computation in Chapter 3

All codes for the Kappa's calculation in the interrater agreement trial are presented in the *Examples* section of the documentation of the `happyr::kappa_tidy()` function. Type `?happyr::kappa_tidy()` to see them.

### Token frequency, type frequency, and type/token ratio analyses in Chapter 5 and 6

The main metaphor data for Chapter 5, 6, and 7 is stored as a tibble in `happyr::phd_data_metaphor`. The relevant function is `happyr::ttr()`. 

```{r ttr, warning = FALSE, message = FALSE}
library(tidyverse)

# calculation for the token, type, and type/token ratios data
ttr_metaphor <- happyr::ttr(df = happyr::phd_data_metaphor,
                            metaphor_var = "metaphors",
                            lexunit_var = "lu",
                            float_digits = 2)
```

The following code retrieve the top-10 metaphors sorted according to their token frequencies.

```{r most-frequent-metaphors}
top_n(x = ttr_metaphor, n = 10L, wt = token) %>% 
  mutate(metaphors = happyr::scaps(metaphors)) %>% # render the metaphors into small capitals
  knitr::kable(caption = "Top-10 most frequent metaphors", row.names = TRUE)
```

From the output of `happyr::ttr()` above (i.e. the `ttr_metaphor` table), we can retrieve the top-10 metaphors with high type frequencies [@rajeg_metaphorical_2018, Ch. 6] with the following codes:

```{r top-10-productive-metaphors}
# sort by type frequency
productive_metaphor <- ttr_metaphor %>% 
  arrange(desc(type_lu)) %>% # sort in descending order for the type frequency
  top_n(10, type_lu) %>% # get the top-10 rows
  mutate(metaphors = happyr::scaps(metaphors)) # small-caps the metaphors

# print as table
productive_metaphor %>% 
select(Metaphors = metaphors,
       Token = token,
       `%Token` = perc_token,
       Type = type_lu,
       `%Type` = perc_type_lu) %>% 
  knitr::kable(caption = 'Top-10 metaphors sorted on their type frequency.', row.names = TRUE)
```

I design a helper function called `happyr::get_lexically_diverse_metaphors()` to retrieve the top-10 lexically diverse or creative metaphors [@rajeg_metaphorical_2018, Ch. 6]. These metaphors are those having relatively high type/token ratios (normalised as percentage) and occurring at least three tokens in the sample.

```{r creative-metaphors}
min_freq <- 3L
ttr_metaphor %>% 
  happyr::get_lexically_diverse_metaphors(min_token = min_freq, top_n_limit = 10L) %>% 
  mutate(metaphors = happyr::scaps(metaphors)) %>% 
  select(Metaphors = metaphors,
         Token = token,
         Type = type_lu,
         `Type/token ratio (in%)` = type_per_token_lu) %>% 
  knitr::kable(caption = paste('Top-10 lexically varied metaphors sorted based on the TTR value and occurring at least ', happyr::numbers2words(min_freq), ' tokens.', sep = ""), row.names = TRUE)
```


### Retrieving the frequency of submappings, semantic source frames, and metaphorical lexical units of metaphors

The data is contained within `happyr::phd_data_metaphor`. Among the relevant functions are `happyr::get_submappings()`, `happyr::get_frames()`, and `happyr::get_lu_table()`. The illustration is based on data for the `r happyr::scaps("happiness is liquid in a container")` metaphor.

```{r submappings-liquid-in-container}
# get the submappings for the liquid in a container
happyr::get_submappings(metaphor = "liquid in a container", df = happyr::phd_data_metaphor) %>% 
  mutate(submappings = happyr::scaps(submappings)) %>% 
  knitr::kable(caption = paste("Submappings for ", happyr::scaps("happiness is liquid in a container."), sep = ""), row.names = TRUE)
```

Column `n` shows the 'token frequency' of the submappings (with `perc` indicates the token's percentage). Meanwhile `type` shows the 'type frequency' of the submappings (i.e., the number of different lexical unit types evoking the corresponding submappings of a given metaphor).

Use `happyr::get_frames()` to retrieve frequency profiles of the source frames for a given metaphor:

```{r frames-liquid-in-container}
# get the source frames evoked by the metaphorical expressions for the liquid in a container
happyr::get_frames(metaphor = "liquid in a container", df = happyr::phd_data_metaphor) %>% 
  mutate(frames = happyr::scaps(frames)) %>% 
  knitr::kable(caption = paste("Source frames for ", happyr::scaps("happiness is liquid in a container."), sep = ""), row.names = TRUE)
```

To print the source frame *lexical units* in the metaphorical expressions, use `happyr::get_lu_table()`:

```{r lu-liquid-in-container}
# print the top-10 Lexical Units of liquid in a container metaphor
happyr::get_lu_table(metaphor = "liquid in a container", 
                     top_n_only = TRUE, 
                     top_n_limit = 10L, 
                     df = happyr::phd_data_metaphor) %>% 
  knitr::kable(caption = paste("Top-10 most frequent lexical units for ", happyr::scaps("happiness is liquid in a container."), sep = ""),
               row.names = TRUE)
```

The column `Perc_overall` indicates the percentage of a given LU from the total tokens of the given metaphor.



### Computing distinctive metaphors and distinctive collocates for Chapter 7

The distinctiveness of a given metaphor and collocate with each happiness synonym is measured using the *Multiple Distinctive Collexeme Analysis* (MDCA) [cf., e.g., @hilpert_distinctive_2006; @hoffmann_collostructional_2013, pp. 299-300]. The MDCA function is available as `happyr::mdca()`.

```{r mdca-metaphors}
# MDCA for metaphor * synonyms with concise output
mdca_res <- happyr::mdca(df = happyr::phd_data_metaphor, coll_var = "metaphors", concise_output = TRUE)
```

The data for the collocates are available in the `happyr::colloc_input_data`. The English gloss/translation for the distinctive collocates are stored in `happyr::dist_colloc_gloss`. 

```{r mdca-collocates}
# mdca for window-span collocational data
mdca_colloc <- happyr::mdca(df = happyr::colloc_input_data, coll_var = "collocates", concise_output = TRUE)
```

Two related functions are available to retrieve the *attracted*/*distinctive* and the *repelled* items from the results of MDCA for the metaphors and collocates. They are `happyr::mdca_attr()` and `happyr::mdca_repel()`. The following example shows how to get the distinctive metaphors for *kebahagiaan* 'happiness' having the association strength of equal to, or greater than, two (i.e. *p*~binomial~ < 0.01):

```{r dist-for-kebahagiaan}
mdca_res %>%
  happyr::mdca_attr(cxn_type = "kebahagiaan", min_assocstr = 2) %>% 
  mutate(exp = round(exp, 3L), # round the expected co-occurrence frequency
         metaphors = happyr::scaps(metaphors)) %>% 
  select(-synonyms) %>%
  as.data.frame() %>% 
  knitr::kable(caption = "Distinctive metaphors for *kebahagiaan* 'happiness'", row.names = TRUE)
```

The `p_holm` column provides the Holm's corrected significance level [@gries_statistics_2009, pp. 249, 251] of the Binomial Test *p*-value (`p_binomial`) used as the basis for the association strength value (`assocstr`) [cf. @hoffmann_collostructional_2013, p. 305], which is derived via the log-transformed *p*~Binomial~-value to the base of 10. The `dec` column indicates the significane of the association between the metaphor and *kebahagiaan* 'happiness' at the corrected level. Column `exp` shows the 'expected' co-occurrence frequency of the metaphor with *kebahagiaan* while `n` is the 'observed' co-occurrence frequency in the sample.

The following code shows how to use `happyr::mdca_repel()` for *kebahagiaan* 'happiness' data:

```{r repel-by-kebahagiaan}
mdca_res %>%
  happyr::mdca_repel(cxn_type = "kebahagiaan", min_assocstr = -2) %>% 
  mutate(exp = round(exp, 3L),
         metaphors = happyr::scaps(metaphors)) %>% 
  select(-synonyms) %>%
  knitr::kable(caption = "Repelled metaphors for *kebahagiaan* 'happiness'", row.names = TRUE)
```

Finally, below is the code to retrieve the top-20 most distinctive collocates co-occurring with *kebahagiaan* 'happiness' within the span of 4 words to the left and right of *kebahagiaan*.

```{r colloc-res-kebahagiaan}
# present the result table for collocational analysis for *kebahagiaan*
happyr::mdca_attr(mdca_colloc, cxn_type = '^kebahagiaan') %>% 
  top_n(20, assocstr) %>% 
  left_join(happyr::dist_colloc_gloss, by = "collocates") %>% # left-join the gloss for the distinctive collocates
  select(-synonyms) %>%
  select(collocates, gloss, everything()) %>%
  mutate(exp = round(exp, 3), 
         collocates = paste("*", collocates, "*", sep = "")) %>%
  knitr::kable(caption="The 20 most distinctive, 4-window span collocates for *kebahagiaan* 'happiness' in the whole Indonesian Leipzig Corpora collection.", row.names = TRUE)
```

## References


