---
output: github_document
link-citations: TRUE
bibliography: 'citation_README.bib'
csl: '/Users/Primahadi/Google Drive/MONASH PhD Journey/3rd Year (mid 2017-mid 2018)/ch6/apa-old-doi-prefix.csl'
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Travis build status](https://travis-ci.org/gederajeg/happyr.svg?branch=master)](https://travis-ci.org/gederajeg/happyr) [![Coverage status](https://codecov.io/gh/gederajeg/happyr/branch/master/graph/badge.svg)](https://codecov.io/github/gederajeg/happyr?branch=master)

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# happyr

The goal of `happyr` is to provide the R functionalities and the required dataset for the quantitative analyses in Rajeg [-@rajeg_metaphorical_2018]. The underlying codes within the package are based on most of the core packages of the [`tidyverse`](https://www.tidyverse.org).

## Installation

You can install the released version of `happyr` from [GitHub](https://github.com/gederajeg/happyr) with the [`remotes`](https://github.com/r-lib/remotes) package:

``` r
# install the `remotes` package
install.packages("remotes") 

# install the `happyr` package
remotes::install_github("gederajeg/happyr@v0.1.0")
```

## Examples

### Interrater-agreement computation in Chapter 3

All codes for the Kappa's calculation in the interrater agreement trial are presented in the *Examples* section of the documentation of the `kappa_tidy()` function. Type `?kappa_tidy()` to see them.

### Token frequency, type frequency, and type/token ratio analyses in Chapter 5 and 6

The main metaphor data for Chapter 5, 6, and 7 is stored as a tibble in `phd_data_metaphor`. The relevant function for the token, type, and type/token ratios analyses in Chapter 5 and 6 is `ttr()`. 

```{r ttr, warning = FALSE, message = FALSE}
# load the required packages
library(happyr)
library(tidyverse)

# calculation for the token, type, and type/token ratios data
ttr_metaphor <- ttr(df = phd_data_metaphor,
                    metaphor_var = "metaphors",
                    lexunit_var = "lu",
                    float_digits = 2)
```

The following code retrieve the top-10 metaphors sorted according to their token frequencies. A function for rendering the metaphors strings as small-capital in the MS Word output is available in the package as `scaps()`.

```{r most-frequent-metaphors}
top_n(x = ttr_metaphor, n = 10L, wt = token) %>% 
  mutate(metaphors = scaps(metaphors)) %>% # render the metaphors into small capitals to be printed in MS Word output
  knitr::kable(caption = "Top-10 most frequent metaphors", row.names = TRUE)
```

From the output of `ttr()` above (i.e. the `ttr_metaphor` table), we can retrieve the top-10 metaphors with high type frequencies [@rajeg_metaphorical_2018, Ch. 6] with the following codes:

```{r top-10-productive-metaphors}
# sort by type frequency
productive_metaphor <- ttr_metaphor %>% 
  arrange(desc(type_lu)) %>% # sort in descending order for the type frequency
  top_n(10, type_lu) %>% # get the top-10 rows
  mutate(metaphors = scaps(metaphors)) # small-caps the metaphors texts

# print as table
productive_metaphor %>% 
select(Metaphors = metaphors,
       Token = token,
       `%Token` = perc_token,
       Type = type_lu,
       `%Type` = perc_type_lu) %>% 
  knitr::kable(caption = 'Top-10 metaphors sorted on their type frequency.', row.names = TRUE)
```

I design a helper function called `get_lexically_diverse_metaphors()` to retrieve the top-10 lexically diverse or creative metaphors [@rajeg_metaphorical_2018, Ch. 6]. These metaphors are those having relatively high type/token ratios (normalised as percentage) and occurring at least three tokens in the sample.

```{r creative-metaphors}
min_freq <- 3L
ttr_metaphor %>% 
  get_lexically_diverse_metaphors(min_token = min_freq, top_n_limit = 10L) %>% 
  mutate(metaphors = scaps(metaphors)) %>% 
  select(Metaphors = metaphors,
         Token = token,
         Type = type_lu,
         `Type/token ratio (in%)` = type_per_token_lu) %>% 
  knitr::kable(caption = paste('Top-10 lexically varied metaphors sorted based on the TTR value and occurring at least ', happyr::numbers2words(min_freq), ' tokens.', sep = ""), row.names = TRUE)
```


#### Retrieving the frequency of submappings, semantic source frames, and metaphorical lexical units of metaphors

The data for retrieving the information on the submappings, source frames, and the lexical units is contained within `phd_data_metaphor`. Among the relevant functions for retrieving these information are `get_submappings()`, `get_frames()`, and `get_lu_table()`. The illustration is based on data for the `r happyr::scaps("happiness is liquid in a container")` metaphor.

```{r submappings-liquid-in-container}
# get the submappings for the liquid in a container
get_submappings(metaphor = "liquid in a container", df = phd_data_metaphor) %>% 
  mutate(submappings = scaps(submappings)) %>% 
  knitr::kable(caption = paste("Submappings for ", scaps("happiness is liquid in a container."), sep = ""), row.names = TRUE)
```

Column `n` shows the 'token frequency' of the submappings (with `perc` indicates the token's percentage). Meanwhile `type` shows the 'type frequency' of the submappings (i.e., the number of different lexical unit types evoking the corresponding submappings of a given metaphor).

Use `get_frames()` to retrieve frequency profiles of the source frames for a given metaphor:

```{r frames-liquid-in-container}
# get the source frames evoked by the metaphorical expressions for the liquid in a container
get_frames(metaphor = "liquid in a container", df = phd_data_metaphor) %>% 
  mutate(frames = scaps(frames)) %>% 
  knitr::kable(caption = paste("Source frames for ", scaps("happiness is liquid in a container."), sep = ""), row.names = TRUE)
```

To print the source frame *lexical units* in the metaphorical expressions of the metaphor, use `get_lu_table()`:

```{r lu-liquid-in-container}
# print the top-10 Lexical Units of liquid in a container metaphor
get_lu_table(metaphor = "liquid in a container", 
             top_n_only = TRUE, 
             top_n_limit = 10L, 
             df = phd_data_metaphor) %>% 
  knitr::kable(caption = paste("Top-10 most frequent lexical units for ",
                               scaps("happiness is liquid in a container."), sep = ""),
               row.names = TRUE)
```

The column `Perc_overall` indicates the percentage of a given LU from the total tokens of the given metaphor. Based on the same data, it is also possible to retrieve a frequency table for the lexical units and the submappings they evoke for a given metaphor. Use `get_lu_submappings_table()` for this purpose. 

```{r lu-submet-liquid-in-container}
get_lu_submappings_table(metaphor = "liquid in a container",
                         df = phd_data_metaphor) %>% 
  mutate(submappings = scaps(submappings), # small-cap the submapping
         lu = paste("*", lu, "*", sep = "")) %>% # italicised the printed lexical units 
  knitr::kable(caption = paste("Evoked submappings for the lexical units of the ",
                               scaps("happiness is liquid in a container"), " metaphor.", sep = ""),
               row.names = TRUE)
```

The column `perc_expr_overall` indicates the percentages of the token frequencies the lexical units for the given metaphor. Meanwhile `perc_expr_by_submappings` indicates the percentages of the lexical units for each submapping of the given metaphor.

### Computing the distinctive metaphors and the distinctive collocates in Chapter 7

The distinctiveness of a given metaphor and collocate with each happiness synonym is measured using the *Multiple Distinctive Collexeme Analysis* (MDCA) [cf., e.g., @hilpert_distinctive_2006; @hoffmann_collostructional_2013, pp. 299-300]. The MDCA function is available as `mdca()`.

```{r mdca-metaphors}
# MDCA for metaphor * synonyms with concise output
mdca_res <- mdca(df = phd_data_metaphor, coll_var = "metaphors", concise_output = TRUE)
```

The data for the collocates are available in the `colloc_input_data`. The English gloss/translation for the distinctive collocates are stored in `dist_colloc_gloss`. 

```{r mdca-collocates}
# mdca for window-span collocational data
mdca_colloc <- mdca(df = colloc_input_data, coll_var = "collocates", concise_output = TRUE)
```

The package also provides two related functions to retrieve the *attracted*/*distinctive* and the *repelled* items from the results of MDCA for the metaphors and collocates. They are `mdca_attr()` and `mdca_repel()`. The following example shows how to get the distinctive metaphors for *kebahagiaan* 'happiness' having the association strength of equal to, or greater than, two (i.e. *p*~binomial~ < 0.01):

```{r dist-for-kebahagiaan}
mdca_res %>%
  mdca_attr(cxn_type = "kebahagiaan", min_assocstr = 2) %>% 
  mutate(exp = round(exp, 3L), # round the expected co-occurrence frequency
         metaphors = scaps(metaphors)) %>% 
  select(-synonyms) %>%
  as.data.frame() %>% 
  knitr::kable(caption = "Distinctive metaphors for *kebahagiaan* 'happiness'", row.names = TRUE)
```

The `p_holm` column provides the Holm's corrected significance level [@gries_statistics_2009, pp. 249, 251] of the Binomial Test *p*-value (`p_binomial`) used as the basis for the association strength value (`assocstr`) [cf. @hoffmann_collostructional_2013, p. 305], which is derived via the log-transformed *p*~Binomial~-value to the base of 10. The `dec` column indicates the significane of the association between the metaphor and *kebahagiaan* 'happiness' at the corrected level. Column `exp` shows the 'expected' co-occurrence frequency of the metaphor with *kebahagiaan* while `n` is the 'observed' co-occurrence frequency in the sample.

The following code shows how to use `mdca_repel()` for *kebahagiaan* 'happiness' data:

```{r repel-by-kebahagiaan}
mdca_res %>%
  mdca_repel(cxn_type = "kebahagiaan", min_assocstr = -2) %>% 
  mutate(exp = round(exp, 3L),
         metaphors = scaps(metaphors)) %>% 
  select(-synonyms) %>%
  knitr::kable(caption = "Repelled metaphors for *kebahagiaan* 'happiness'", row.names = TRUE)
```

Finally, below is the code to retrieve the top-20 most distinctive collocates co-occurring with *kebahagiaan* 'happiness' within the span of 4 words to the left and right of *kebahagiaan*.

```{r colloc-res-kebahagiaan}
# present the result table for collocational analysis for *kebahagiaan*
mdca_attr(mdca_colloc, cxn_type = '^kebahagiaan') %>% 
  top_n(20, assocstr) %>% 
  left_join(dist_colloc_gloss, by = "collocates") %>% # left-join the gloss for the distinctive collocates
  select(-synonyms) %>%
  select(collocates, gloss, everything()) %>%
  mutate(exp = round(exp, 3), 
         collocates = paste("*", collocates, "*", sep = "")) %>%
  knitr::kable(caption="The 20 most distinctive, 4-window span collocates for *kebahagiaan* 'happiness' in the whole Indonesian Leipzig Corpora collection.", row.names = TRUE)
```

## References


