---
output: github_document
link-citations: TRUE
bibliography: 'citation_README.bib'
csl: 'apa-old-doi-prefix.csl'
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Travis build status](https://travis-ci.org/gederajeg/happyr.svg?branch=master)](https://travis-ci.org/gederajeg/happyr) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/gederajeg/happyr?branch=master&svg=true)](https://ci.appveyor.com/project/gederajeg/happyr) [![Coverage status](https://codecov.io/gh/gederajeg/happyr/branch/master/graph/badge.svg)](https://codecov.io/github/gederajeg/happyr?branch=master)

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.618,
  fig.align = "center",
  dpi = 300,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "90%"
)
```
# happyr

The goal of `happyr` is to document the R codes and the required dataset for the quantitative analyses in Rajeg's [-@rajeg_metaphorical_2018] PhD thesis (submitted for examination on 28 September 2018). The study focuses on metaphors for `r scapr::scaps("happiness")` near-synonyms in Indonesian. The corpus data for the study mainly come from the *Indonesian Leipzig Corpora Collection* [@quasthoff_indonesian_2013; @goldhahn_building_2012; @biemann_leipzig_2007]. The Leipzig Corpora are freely available for [download](http://wortschatz.uni-leipzig.de/en/download) and their use is licensed under the Creative Common License [CC-BY](https://creativecommons.org/licenses/by/4.0/) (see the [Terms of Usage](http://wortschatz.uni-leipzig.de/en/usage) page for further details). 

The `happyr` package is based on the core packages in the [`tidyverse`](https://www.tidyverse.org), and is built under R version 3.5.1 (2018-07-02) -- "Feather Spray" (see the **Session Info** section at the bottom of the page for further details on the dependencies).

## Acknowledgement

The thesis is supervised by Dr. [Alice Gaby](http://profiles.arts.monash.edu.au/alice-gaby/) (main), Dr. [Howard Manns](http://profiles.arts.monash.edu.au/howard-manns/) (associate), and Dr. [Simon Musgrave](http://profiles.arts.monash.edu.au/simon-musgrave/) (associate). The panel members during the author's candidature milestones consist of Dr. [Anna Margetts](http://profiles.arts.monash.edu.au/anna-margetts/), Dr. [Réka Benczes](https://www.researchgate.net/profile/Reka_Benczes), and Prof. [John Newman](http://profiles.arts.monash.edu.au/john-newman/). The thesis is fully funded by [Monash University](https://www.monash.edu), Australia through the [International Graduate Research Scholarships](https://www.monash.edu/graduate-research/future-students/scholarships) schemes (i.e. _Monash International Postgraduate Research Scholarships_ (MIPRS, now MITS) and _Monash Graduate Scholarships_ (MGS)).

## Installation

The `happyr` package can be installed from [GitHub](https://github.com/gederajeg/happyr) with the [`devtools`](https://cran.r-project.org/package=devtools) package:

``` r
# install the `devtools` package
install.packages("devtools") 

# install the `happyr` package
devtools::install_github("gederajeg/happyr")
```

## Examples

```{r load-packages}
# load the required packages
library(happyr)
library(tidyverse)
```


### Interrater-agreement computation in Chapter 3

All codes for the Kappa's calculation in the interrater agreement trial are presented in the *Examples* section of the documentation of the `kappa_tidy()` function. Type `?kappa_tidy()` to see them.

The `ggplot2` code for producing Figure 3.1 in Rajeg [-@rajeg_metaphorical_2018, Ch. 3] is wrapped into a function called `plot_cxn_interrater()`. The input data frame is `top_cxn_data`.

```{r cxn-interrater-figure, fig.asp = 0.75, fig.width = 6.5}
# prepare plot title and caption
plot_title <- expression(paste("Distribution of the constructional patterns for the agreed cases (", N["patterns"] >= "5)", sep = ""))

plot_caption <- "The values inside the bars are the token frequency of the patterns"
  
plot_cxn_interrater(df = top_cxn_data) +
  # add plot title and caption
  labs(title = plot_title,
       caption = plot_caption) +
  # adjust the size of the plot title and caption
  theme(plot.title = element_text(size = 10),
        plot.caption = element_text(size = 7))
```


### Token frequency, type frequency, and type/token ratio analyses in Chapter 5 and 6

The main metaphor data for Chapter 5, 6, and 7 is stored as a tibble in `phd_data_metaphor`. The relevant function for the token, type, and type/token ratios analyses in Chapter 5 and 6 is `ttr()`. 

```{r ttr, warning = FALSE, message = FALSE}
# calculation for the token, type, and type/token ratios
ttr_metaphor <- ttr(df = phd_data_metaphor,
                    metaphor_var = "metaphors", # specify col.name of the metaphor variable
                    lexunit_var = "lu", # specify col.name of the lexical unit variable
                    float_digits = 2)
```

The following code retrieves the top-10 metaphors sorted according to their token frequencies. A function for rendering the metaphors strings as small-capital in the MS Word output is available in the package as `scaps()`; keyboard shortcut to produce the so-called "pipe" `%>%` is `Ctrl + Shift + M` (on Windows) or `Cmd + Shift + M` (on macOS).

```{r most-frequent-metaphors}
top_n(x = ttr_metaphor, n = 10L, wt = token) %>% 
  mutate(metaphors = scaps(metaphors)) %>% # render the metaphors into small capitals to be printed in MS Word output
  knitr::kable(caption = "Top-10 most frequent metaphors", row.names = TRUE)
```

The column `token` shows the token frequency of a metaphor meanwhile the column `type_lu` represents the number of different lexical-unit types evoking the source domain frames of the metaphor in the metaphorical expressions. The original values of the `type_per_token_lu` are normalised into the number of type per 100 tokens [cf. @oster_emotions_2018, pp. 206-207]. Thus, the closer the TTR of a metaphor to 100, the higher the rate of different lexical-unit type per 100 tokens of the metaphor (see further below) [@stefanowitsch_corpus-based_2016, pp. 118-120; @stefanowitsch_corpus_2017, p. 282; @oster_emotions_2018, p. 206; @oster_using_2010, pp. 748-749]. From the output of `ttr()` above (i.e. the `ttr_metaphor` table), we can retrieve the top-10 metaphors with high type frequencies with the following codes [@rajeg_metaphorical_2018, Ch. 6]:

```{r top-10-productive-metaphors}
# sort by type frequency
productive_metaphor <- ttr_metaphor %>% 
  arrange(desc(type_lu)) %>% # sort in descending order for the type frequency
  top_n(10, type_lu) %>% # get the top-10 rows
  mutate(metaphors = scaps(metaphors)) # small-caps the metaphors texts

# print as table
productive_metaphor %>% 
select(Metaphors = metaphors,
       Token = token,
       `%Token` = perc_token,
       Type = type_lu,
       `%Type` = perc_type_lu) %>% 
  knitr::kable(caption = 'Top-10 metaphors sorted on their type frequency.', row.names = TRUE)
```

I design a helper function called `get_lexically_diverse_metaphors()` to retrieve the top-10 lexically diverse or creative metaphors [@rajeg_metaphorical_2018, Ch. 6]. These metaphors are those having relatively high type/token ratios and occurring at least three tokens in the sample.

```{r creative-metaphors}
min_freq <- 3L
ttr_metaphor %>% 
  get_lexically_diverse_metaphors(min_token = min_freq, top_n_limit = 10L) %>% 
  mutate(metaphors = scaps(metaphors)) %>% 
  select(Metaphors = metaphors,
         Token = token,
         Type = type_lu,
         `Type/token ratio` = type_per_token_lu) %>% 
  knitr::kable(caption = paste('Top-10 lexically varied metaphors sorted based on the TTR value and occurring at least ', happyr::numbers2words(min_freq), ' tokens.', sep = ""), row.names = TRUE)
```

One way to interpret the values in the `Type/token ratio` (TTR) column is to conceive them as representing the number of unique lexical-unit types per 100 tokens of a metaphor. The higher the ratio, the more creative a given metaphor is linguistically expressed. For instance, the TTR value of `r happyr::scaps("happiness is an adversary")` (i.e. `r unlist(ttr_metaphor[ttr_metaphor$metaphors=="happiness is an adversary", "type_per_token_lu"])`) indicates that there are about `r unlist(ttr_metaphor[ttr_metaphor$metaphors=="happiness is an adversary", "type_per_token_lu"])` unique types per 100 tokens of the `r happyr::scaps("happiness is an adversary")`, which is much higher than the TTR value of `r scaps("happiness is a possessable object")` (i.e. `r unlist(ttr_metaphor[ttr_metaphor$metaphors=="happiness is a possessable object", "type_per_token_lu"])`). The TTR value of a metaphor is used to represent the *creativity ratio* of a metaphor in its linguistic manifestation [cf. @oster_emotions_2018, p. 206; @oster_using_2010, pp. 748-749].

#### Retrieving the frequency of submappings, semantic source frames, and lexical units of metaphors

The data for retrieving the information on the submappings, source frames, and the lexical units is contained within `phd_data_metaphor`. Among the relevant functions for retrieving these information are `get_submappings()`, `get_frames()`, and `get_lu_table()`. The illustration is based on data for the `r happyr::scaps("happiness is liquid in a container")` metaphor.

```{r submappings-liquid-in-container}
# get the submappings for the liquid in a container
get_submappings(metaphor = "liquid in a container", df = phd_data_metaphor) %>% 
  mutate(submappings = scaps(submappings)) %>% 
  knitr::kable(caption = paste("Submappings for ", scaps("happiness is liquid in a container."), sep = ""), row.names = TRUE)
```

Column `n` shows the 'token frequency' of the submappings (with `perc` indicates the token's percentage). Meanwhile `type` shows the 'type frequency' of the submappings (i.e., the number of different lexical unit types evoking the corresponding submappings of a given metaphor).

Use `get_frames()` to retrieve frequency profiles of the source frames for a given metaphor:

```{r frames-liquid-in-container}
# get the source frames evoked by the metaphorical expressions for the liquid in a container
get_frames(metaphor = "liquid in a container", df = phd_data_metaphor) %>% 
  mutate(frames = scaps(frames)) %>% 
  knitr::kable(caption = paste("Source frames for ", scaps("happiness is liquid in a container."), sep = ""), row.names = TRUE)
```

To print the source frame *lexical units* in the metaphorical expressions of the metaphor, use `get_lu_table()`:

```{r lu-liquid-in-container}
# print the top-10 Lexical Units of liquid in a container metaphor
get_lu_table(metaphor = "liquid in a container", 
             top_n_only = TRUE, 
             top_n_limit = 10L, 
             df = phd_data_metaphor) %>% 
  knitr::kable(caption = paste("Top-10 most frequent lexical units for ",
                               scaps("happiness is liquid in a container."), sep = ""),
               row.names = TRUE)
```

The column `Perc_overall` indicates the percentage of a given LU from the total tokens of the given metaphor. Based on the same data, it is also possible to retrieve a frequency table for the lexical units and the submappings they evoke for a given metaphor. Use `get_lu_submappings_table()` for this purpose. 

```{r lu-submet-liquid-in-container}
get_lu_submappings_table(metaphor = "liquid in a container",
                         df = phd_data_metaphor) %>% 
  mutate(submappings = scaps(submappings), # small-cap the submapping
         lu = paste("*", lu, "*", sep = "")) %>% # italicised the printed lexical units 
  knitr::kable(caption = paste("Evoked submappings for the lexical units of the ",
                               scaps("happiness is liquid in a container"), " metaphor.", sep = ""),
               row.names = TRUE)
```

The column `perc_expr_overall` indicates the percentages of the token frequencies of the lexical units for the given metaphor. Meanwhile `perc_expr_by_submappings` indicates the percentages of the lexical units for each submapping of the given metaphor.

#### Visualising the frequency of occurrences for the body-part terms in the metaphorical expressions

The function for generating Figure 5.1 in Chapter 5 is `plot_body_part()` with `phd_data_metaphor` as the only input argument:

```{r body-part-figure, fig.asp = 0.7, fig.width = 6.5}
plot_body_part(df = phd_data_metaphor)
```

The following codes are used to generate the most-frequent co-occurrence of body-part terms and metaphors in Chapter 5:

```{r body-metaphors-frequency-table}
# body-part gloss
bp_gloss <- tibble(gloss = c('chest/bosom', 'self', 'liver', 'eyes', 'face', 'body', 'face', 'face', 'deepest part of the heart', 'lips', 'mouth', 'body; bodily'), 
                   body_part_terms = c('dada', 'diri', 'hati', 'mata', 'muka', 'tubuh', 'wajah', 'paras', 'lubuk kalbu', 'bibir', 'mulut', 'jasmani'))

# generate the table
phd_data_metaphor %>% 
  filter(body_part_inclusion %in% c('y')) %>% 
  count(body_part_terms, metaphors) %>% 
  arrange(desc(n)) %>% 
  left_join(bp_gloss, by = 'body_part_terms') %>% # join the glossing tibble
  select(metaphors, body_part_terms, gloss, n) %>% 
  mutate(metaphors = scaps(metaphors), 
         body_part_terms = paste("*", body_part_terms, "* '", gloss, "'", sep = "")) %>%
  select(Body_parts = body_part_terms, Metaphors = metaphors, N = n) %>%
  top_n(10, N) %>%
  knitr::kable(caption = 'The ten most frequent <span style="font-variant:small-caps;">Body-part</span>`*`<span style="font-variant:small-caps;">Metaphors</span> co-occurrence for <span style="font-variant:small-caps;">Happiness</span> in Indonesian.', row.names = TRUE)
```


### Identifying the distinctive metaphors and the distinctive collocates in Chapter 7

The distinctiveness of a given metaphor and collocate with each happiness synonym is measured using *Multiple Distinctive Collexeme Analysis* (MDCA) [cf., e.g., @hilpert_distinctive_2006; @hoffmann_collostructional_2013, pp. 299-300]. The MDCA function is available as `mdca()`.

```{r mdca-metaphors}
# MDCA for metaphor * synonyms with concise output
mdca_res <- mdca(df = phd_data_metaphor, cxn_var = "synonyms", coll_var = "metaphors", concise_output = TRUE)
```

The data for the collocates are available in the `colloc_input_data`. The English gloss/translation for the distinctive collocates are stored in `dist_colloc_gloss`. 

```{r mdca-collocates}
# mdca for window-span collocational data
mdca_colloc <- mdca(df = colloc_input_data, cxn_var = "synonyms", coll_var = "collocates", concise_output = TRUE)
```

The package also provides two related functions to retrieve the *attracted*/*distinctive* and the *repelled* items from the results of MDCA. They are `mdca_attr()` and `mdca_repel()`. The following example shows how to get the distinctive metaphors for *kebahagiaan* 'happiness' having the association strength of equal to, or greater than, two (i.e. *p*~binomial~ < 0.01):

```{r dist-for-kebahagiaan}
mdca_res %>%
  mdca_attr(cxn_type = "kebahagiaan", min_assocstr = 2) %>% 
  mutate(exp = round(exp, 3L), # round the expected co-occurrence frequency
         metaphors = scaps(metaphors)) %>% 
  select(-synonyms) %>%
  as.data.frame() %>% 
  knitr::kable(caption = "Distinctive metaphors for *kebahagiaan* 'happiness'", row.names = TRUE)
```

The `p_holm` column provides the Holm's corrected significance level [@gries_statistics_2009, pp. 249, 251] of the Binomial Test *p*-value (`p_binomial`). The Binomial *p*-value is used as the basis for the association strength value (`assocstr`) [cf. @hoffmann_collostructional_2013, p. 305], which is derived via the log-transformed *p*~Binomial~-value to the base of 10. The `dec` column indicates the significane of the association between the metaphor and *kebahagiaan* 'happiness' at the corrected level. Column `exp` shows the 'expected' co-occurrence frequency of the metaphor with *kebahagiaan* while `n` is the 'observed' co-occurrence frequency in the sample.

The following code shows how to use `mdca_repel()` for retrieving the repelled metaphors by *kebahagiaan* 'happiness':

```{r repel-by-kebahagiaan}
mdca_res %>%
  mdca_repel(cxn_type = "kebahagiaan", min_assocstr = -2) %>% 
  mutate(exp = round(exp, 3L),
         metaphors = scaps(metaphors)) %>% 
  select(-synonyms) %>%
  knitr::kable(caption = "Repelled metaphors for *kebahagiaan* 'happiness'", row.names = TRUE)
```

Finally, below is the code to retrieve the top-20 most distinctive collocates co-occurring with *kebahagiaan* 'happiness' within the span of 4 words to the left and right of *kebahagiaan*.

```{r colloc-res-kebahagiaan}
# present the result table for collocational analysis of *kebahagiaan*
mdca_attr(mdca_colloc, cxn_type = '^kebahagiaan') %>% 
  top_n(20, assocstr) %>% 
  left_join(dist_colloc_gloss, by = "collocates") %>% # left-join the gloss for the distinctive collocates
  select(-synonyms) %>%
  select(collocates, gloss, everything()) %>%
  mutate(exp = round(exp, 3), 
         collocates = paste("*", collocates, "*", sep = "")) %>%
  knitr::kable(caption="The 20 most distinctive, 4-window span collocates for *kebahagiaan* 'happiness' in the whole Indonesian Leipzig Corpora collection.", row.names = TRUE)
```

## Session info {#sessioninfo}
```{r sess-info}
devtools::session_info()
```


## References


